Converging High-Throughput and High-Performance Computing Paradigms: \\ A Case Study of Using Abstractions to Bridge the Divide

### 2017-03-12 nge.tex
Typos

\mtnote{NOTE: I do not mention backfill availability Vs normal availability (i.e., submitting to the queue a `normal' job) because, in theory, the design of PanDA Broker enable this capability. I would speak about about backfill/not backfill in the discussion of NGE, when speaking about its generality. Part of this generality, is being able to submit to whatever batch system is supported by SAGA, including Titan's PBS and all its queues.}

>>>>

\mtnote{NOTE: I do not mention backfill availability Vs normal availability
(i.e., submitting to the queue a `normal' job) because, in theory, the design of
PanDA Broker enables this capability. I would speak about about backfill/not
backfill in the discussion of NGE, when speaking about its generality. Part of
this generality is being able to submit to whatever batch system is supported by
SAGA, including Titan's PBS and all its queues.}
